Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-09 MS/supp.Rmd
Adding supp download data code

Throughout the supplement R code is contained within code blocks. We provide example data associated with this tutorial which readers can find on the [Open Science Framework](https://osf.io/wscz5/). Importantly, all relevant code chunks have a 'copy and paste' button in the top right corner so that the code can be easily transferred to your own R console.

@@

Before embarking on the case studies readers will need to load the data along with the necessary R packages. Be sure to set your working directory to the folder or locations where you have put the data.

```{r loadpackages, echo = TRUE, class.source='klippy'}
pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd)

@@

@@

# Case Study 2:
```{r class.source='klippy'}

>>>>

Throughout the supplement R code is contained within code blocks. We provide example data associated with this tutorial which readers can find on the [Open Science Framework](https://osf.io/wscz5/), but the code chunks should automatically download and load these for you. Importantly, all relevant code chunks have a 'copy and paste' button in the top right corner so that the code can be easily transferred to your own R console.

@@

Before embarking on the case studies readers will need to load the necessary R packages.

```{r loadpackages, echo = TRUE, class.source='klippy'}
pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here)

@@

# Example on how to download and load for reader. Should work anyway. Needs some testing
download.file(url="https://ndownloader.figshare.com/files/7714777", destfile = "CaseStudy1.csv")

data_CS1 <- read.csv(here("CaseStudy1.csv"))

@@

# Case Study 2:
```{r class.source='klippy'}
download.file(url="REPLACE URL FROM OSF HERE", destfile = "CaseStudy2.csv")

data_CS1 <- read.csv(here("CaseStudy2.csv"))
